Model of lens candidates from Space Warps CFHTLS

### 2016-07-12 paper2.tex
my hands are typing words

Section~\ref{sec:spl} summarises the SpaghettiLens system and
discusses its ongoing development. A SpaghettiLens model consists of a
statistical ensemble of free-form maps of the sky-projected mass
distribution responsible for lensing.  Each lens candidates in
practice gets modelled several times in a collaborative refinement
process\footnote{See ``Collaborative gravitational lens
  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
  the model tree.}  In this paper we report the most recent model for
each lens, as representing a consensus among modellers, as to the best
that could be achieved with the available data and software.
Photometric lens redshifts are used; source redshifts are set to
$z=2$.  The models can, however, be trivially rescaled to use better
redshift values, as and when they become available.
\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
identified some areas for improvement.  The first two of those are
taken up in Section~\ref{sec:spl}, along with a further idea.  In
\S~\ref{subsec:hires} we show that making mass maps fine-grained in
the central region relieves a tendency in the earlier work for mass to
be too shallow. \S~\ref{subsec:sourcefit} we introduce fitting of the
brightness profiles of the source.  This feature has not yet been
included in SpaghettiLens, but has been done for in post-processing
for a few especially interesting candidates. Then in
\S~\ref{subsec:parameter} we consider the possibility of fitting a
parametric lens model to the model ensemble; so far we have only been
successful at extracting an Einstein radius.

Section~\ref{sec:stellar-mass} is about stellar mass.

Section~\ref{sec:examples} discusses ten systems in detail.

Section~\ref{sec:summary} has a summary table.

@@

\cite{2015MNRAS.447.2170K} introduced and implemented two
main ideas. One is a `spaghetti diagram,' which is a cartoon-like
markup of a candidate lensing system which encodes a proposal for its
mass distribution.  It enables volunteers to interact with a
server-side numerical engine \citep[GLASS, developed
  by][]{2014MNRAS.445.2181C} in an intuitive way.  The other new idea
was a `model tree' --- a volunteer can model a lens from scratch, or
they can modify an existing model and thus try to improve upon it.
This facility, in conjunction with forum discussion, enables
development trees of models.  The models reported in this paper are
the most recent ones for each lens candidate, but typically they are
descended from previous models through the contributions of more than
one individual.

\subsection{HiRes / Subsampling of central region}\label{subsec:hires}

@@

\subsection{Additional / Improved Synthetic Image}\label{subsec:sourcefit}

Volunteers often ask about better indicators to identify wether the modelling resulted in a ``good'' or ``bad'' model.
We developped a prototype of a better syntetic image than just the rendering of a \todo{insert currently used source profile} profile.
It operates on the composite input image.
The user has to mask the supposed lensed images.
The algorith then establishes a grid on the source plane and projects the masked pixels of the lense plane back to the source plane.
Multiple lens plane pixels fall onto one source plane pixel and get averaged.
The new synthetic image then reverses the mapping, coloring each pixel in the lens plane with the corresponding values of the source plane pixel.

@@

In this section we show modelling results for ten of the lens
candidates.  The first five (see Figures~\figref{SW05}--\figref{SW29})
are the most convincingly modelled systems.  The next three cases
(Figures~\figref{SW42},\figref{SW58}) are less good but still very
plausible models, and are representative of the majority of the
sample.  The last two are examples where the models were unconvincing
(Figures~\figref{SW36}) or completely failed (\figref{SW57}).

@@

\subsection{Table}

@@

\appendix

\section{Some extra material}

If you want to present additional material which would interrupt the flow of the main paper,
it can be placed in an Appendix which appears after the list of references.

>>>>

Section~\ref{sec:spl} summarises the SpaghettiLens system and
discusses its ongoing development. A SpaghettiLens model consists of a
statistical ensemble of free-form maps of the sky-projected mass
distribution responsible for lensing.  Each lens candidates in
practice gets modelled several times in a collaborative refinement
process\footnote{See ``Collaborative gravitational lens
  modelling\dots'' in {\tt http://letters.zooniverse.org} especially
  the model tree.}  In this paper we report the most recent model for
each lens, as representing a consensus among modellers, as to the best
that could be achieved with the available data and software.
Photometric lens redshifts are used; source redshifts are set to
$z=2$.  The models can, however, be trivially rescaled to use better
redshift values, as and when they become available.
\cite{2015MNRAS.447.2170K} tested the system on simulated lenses and
identified some areas for improvement.  The first two of those are
taken up in Section~\ref{sec:spl}, along with a further idea. In
\S~\ref{subsec:sourcefit} we introduce fitting of the brightness
profiles of the source.  This feature has not yet been included in
SpaghettiLens, but has been carried out in post-processing for a few
especially interesting candidates.  In \S~\ref{subsec:hires} we show
that making mass maps fine-grained in the central region relieves a
tendency in the earlier work for mass to be too shallow. Then in
\S~\ref{subsec:parameter} we consider the possibility of fitting a
parametric lens model to the model ensemble; so far we have only been
successful at extracting an Einstein radius.

Section~\ref{sec:stellar-mass} explains how we compare the lensing
mass with the mass in stars in the lensing galaxy.  We estimate the
stellar mass by comparing galaxy magnitudes from the CFHTLS pipeline
with the well-known stellar-population models of
\cite{2003MNRAS.344.1000B}.  We then extrapolate the stellar masses to
a halo mass using the abundance-matching prescription of
\cite{2010ApJ...710..903M}.  Naturally, the lensing mass must be more
than the stellar mass but no more than the total halo mass.  We then
introduce what we call a halo index $\haloindex$ which gives an idea
of how the lensing mass compares with these two bounds.

Section~\ref{sec:examples} discusses ten of the systems, including six
systems we found to be particularly interesting.  The online
supplement gives results for all the modelled systems.

In Section~\ref{sec:summary} and Table~\ref{tab:models} we display a
concise characterisation of each modelled system, according to the
image morphology and how clear or indistinct it is, whether the mass
map and synthetic lensed image appear to be plausible, and how the
model mass compares with the estimated stellar and full-halo masses.

@@

A modeller's main input to SpaghettiLens is a sketch of arrival-time
contours on a lensed system.  It gives the locations (or best-guess
locations) of images of point-like sources, along with their ordering
in arrival time, and their parities (minumum, saddle-point or
maximum).  Such a sketch, which we call a spaghetti diagram, tends to
resemble the form of lensed arcs, but it also in effect encodes
encodes a proposal for its mass distribution.  A spaghetti diagram is
read by a server-side numerical engine \citep[GLASS, developed
  by][]{2014MNRAS.445.2181C} which then returns a statistical ensemble
of mass maps.  The mass maps are made up of mass tiles and are
free-form, except that they are required to be concentrated around the
identified lens centre.  They are also required to reproduce the given
image locations, parities and time ordering exactly.  Graphical
representations of the mass map and arrival-time surface are returned
to the user for review.  The user can post these results on a forum,
or discard them and try again.  Volunteers can start the modelling
process afresh, or they can take an existing model from the forum and
modify its input spaghetti diagram or its accompanying options, and
thus obtain a revised model.

\subsection{Improved synthetic images}\label{subsec:sourcefit}

Volunteers often ask about better indicators to identify wether the
modelling resulted in a ``good'' or ``bad'' model.  We developed a
prototype of a better syntetic image than just the rendering of a
conical profile.  It operates on the composite input image.  The user
has to mask the supposed lensed images.  The algorithm then
establishes a grid on the source plane and projects the masked pixels
of the lense plane back to the source plane.  Multiple lens plane
pixels fall onto one source plane pixel and get averaged.  The new
synthetic image then reverses the mapping, coloring each pixel in the
lens plane with the corresponding values of the source plane pixel.

\subsection{Sub-sampling of central region}\label{subsec:hires}

@@

@@

In this section we show modelling results for ten of the lens
candidates.  The first five (see Figures~\figref{SW05}--\figref{SW29})
are the most convincingly modelled systems.  The next three cases
(Figures~\figref{SW42}--\figref{SW19}) are less good but still very
plausible models, and are representative of the majority of the
sample.  The last two are examples where the models were unconvincing
(Figures~\figref{SW36}) or completely failed (\figref{SW57}).

@@

@@

% \appendix
